Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia

### 2017-06-28 doc/manuscript/manuscript.Rmd
Add community-graph figure

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amadarasa
    email: bamadarasa2@unl.edu
    affiliation: 1
  - name: R. Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
# author_summary: |
#   Lorem ipsum dolor sit amet, consectetur adipiscing elit.
header-includes: >
  \usepackage{indentfirst}
bibliography: mybibfile.bib
biblio-style: apalike
output: 
  rticles::peerj_article:
    citation_package: natbib
    base_format: bookdown::pdf_document2 # for using \@ref()
---

@@

Sclerotia are capable of surviving more than five years in soil (Steadman, 1983) and germinate carpogenically or myceliogenically to infect the plant when environmental conditions are favorable.
A carpogenically geminated sclerotia gives rise to apothecia in which ascospores are formed.
Ascospores infect senescent plant tissues that, when supplemented with cool and humid microclimate within the plant canopy, leads to mycelial infection of the host plant.
Consequently, flowering, which coincide with canopy closure is a critical factor of disease initiation since sensing flower parts fallen on to leaves, petioles or stems provide the required energy source for plant infection.
Myceliogenically geminated sclerotia result in formation of hyphae, which also have potential for directly plant infection, though this is considered rare and less important within the disease cycle of the pathogen (Abawi and Grogan, 1975).
Diseased bean fields initially show scattered wilted leaves.
Symptoms on individual plants are water-soaked lesions on leaves, pods and stems, which expand over time and show signs of white fungal mycelia.
Lesions on stems and branches become necrotic as they age and dead tissues appear bleached.
Sclerotia are often produced on dead or dying plants once conditions become unfavorable for fungal growth.

@@

deleteme: @Dirac1953888

@@

Community analysis of the MLGs shared between populations revealed 4 communities with a modularity of 0.17 (Fig. 3Z): A coastal community (CA, OR, WA, and NY), a mid-west community (CO, NE, ND, MI), and an international community (MN, France, Australia).
Analysis with 16 loci resulted in the removal of the NY node because it no longer shared a genotype with OR, but the same overall community structure was present with a modularity of 0.2 (Supplementary Figure S1Z).
The international community appears to be driven by MLG 4, which is shared between all three populations and has a Psex value of 2.87 x 10-5, in contrast to the abundant MLG 25, which has a Psex value of 0.0168.

>>>>

---
title: Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia
preprint: false
author:
  - name: Zhian N. Kamvar
    email: zkamvar@unl.edu
    affiliation: 1
  - name: Bimal Sajeewa Amadarasa
    email: bamadarasa2@unl.edu
    affiliation: 1
  - name: R. Jhala
    email: rjhala2@unl.edu
    affiliation: 1
  - name: James Steadman
    email: jsteadman1@unl.edu
    affiliation: 1
  - name: Sydney E. Everhart
    email: everhart@unl.edu
    affiliation: 1
    corresponding: true
affiliation:
  - code: 1
    address: Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln 68583
abstract: >
  `r paste(readLines("abstract.md"), collapse = "\n  ")`
# author_summary: |
#   Lorem ipsum dolor sit amet, consectetur adipiscing elit.
header-includes: >
  \usepackage{indentfirst}
bibliography: mybibfile.bib
output: 
  rticles::peerj_article:
    citation_package: natbib
    base_format: bookdown::pdf_document2 # for using \@ref()
---

```{r setup, include = FALSE, echo = FALSE}
knitr::opts_knit$set(eval.after = c('fig.cap', 'fig.scap'))
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

@@

Sclerotia are capable of surviving more than five years in soil (Steadman, 1983) and germinate carpogenically or myceliogenically to infect the plant when environmental conditions are favorable.
A carpogenically germinated sclerotia gives rise to apothecia in which ascospores are formed.
Ascospores infect senescent plant tissues that, when supplemented with cool and humid micro-climate within the plant canopy, leads to mycelial infection of the host plant.
Consequently, flowering, which coincide with canopy closure is a critical factor of disease initiation since sensing flower parts fallen on to leaves, petioles or stems provide the required energy source for plant infection.
Myceliogenically germinated sclerotia result in formation of hyphae, which also have potential for directly plant infection, though this is considered rare and less important within the disease cycle of the pathogen (Abawi and Grogan, 1975).
Diseased bean fields initially show scattered wilted leaves.
Symptoms on individual plants are water-soaked lesions on leaves, pods and stems, which expand over time and show signs of white fungal mycelia.
Lesions on stems and branches become necrotic as they age and dead tissues appear bleached.
Sclerotia are often produced on dead or dying plants once conditions become unfavorable for fungal growth.

@@

@@

Community analysis of the MLGs shared between populations revealed 4 communities with a modularity of 0.17 (Fig. \@ref(community-graph)): A coastal community (CA, OR, WA, and NY), a mid-west community (CO, NE, ND, MI), and an international community (MN, France, Australia).
Analysis with 16 loci resulted in the removal of the NY node because it no longer shared a genotype with OR, but the same overall community structure was present with a modularity of 0.2 (Supplementary Figure S1Z).
The international community appears to be driven by MLG 4, which is shared between all three populations and has a Psex value of 2.87 x 10-5, in contrast to the abundant MLG 25, which has a Psex value of 0.0168.

![Network of populations (nodes/circles) and their shared multilocus haplotypes (MLG) (edges/lines) genotyped over 11 loci. 
Each node is labeled with **name (number of MLGs shared/number of MLGs total).** 
The shade and area of the nodes are proportional to the number of unique MLGs within the node and the inner nodes are proportional to the number of private MLGs to the region. 
Each edge represents a single MLG where its thickness represents the number of populations that share the MLG and the shade represents the value of $P_{sex}$, or the probability of encountering that MLG from two independent meiotic events.
](../../results/figures/publication/Figure3Z.pdf){#community-graph width=50%}
